Page not found

### 2023-06-25 manuscript/chapters/3_mappings.qmd
fixed typos
added mean position, fixed typo

1. Create a grid of $2^n \times 2^n = 4^n$ squares of size $2^{-n} \times 2^{-n}$ in the $[0,1]\times[0,1]$ embedding. Each square is located by a position $\vec{v_i} = (v_{1,i},v_{2,i}),\,i\in\{1,\cdots\,2^n\}$.
2. Compute a discretized version of the 1D connectivity kernel
   $$
   \begin{aligned}
   \tilde w(\alpha_i, \beta_j) &= \tilde J_{\alpha_i,\beta_j}\\
   &= \tilde J_{S(i),S(j)}\\
   &\stackrel{\text{def}}{=} J_{ij}\\
   &= w_U(\vec{v_i}, \vec{v_j})
   \end{aligned}
   $$
   for every pair of square locations (where we denote for simplicity of notation $S(i)=S(\vec{v_i})$).
3. Simulate the neural field in $[0,1]$ on the corresponding discretized space, with a mesh size $4^{-n}$.

@@

```{python}
#| label: fig-averaging-geom
#| fig-cap: Square populations corresponding to the segment populations before coarse-graining are colored identically when they are the same bin of 1D length $2^{-n}$. Here we show $n=3$.
#| fig-subcap:
#|   - Z-mapping
#|   - Column mapping
#| layout-ncol: 2
#| echo: false

@@

	fig, ax = plt.subplots()
	ax.plot(*F.T, color='gray')
	colors = cycle(['#750087','#001997','#06bd01','#ffff00','#fe941e','#ff1e26','#fcaec5','#74d4ea','#603814','#010101','#fbf7f4'])
	for i in range(2**nrec): ax.scatter(*F_[i, :, :].T, zorder=10, color=next(colors), ec='k')
	ax.set(
		xlim=(0,1), ylim=(0,1),
		xlabel='$v_1$', ylabel='$v_2$', aspect='equal',
		xticks=[0, 0.25, 0.5, 0.75, 1], yticks=[0, 0.25, 0.5, 0.75, 1])
	mktrans(fig, ax)
	breathe(ax)
	return fig, ax

>>>>

1. Create a grid of $2^n \times 2^n = 4^n$ squares of size $2^{-n} \times 2^{-n}$ in the $[0,1]\times[0,1]$ embedding. Each square is located by a position $\vec{v_i} = (v_{1,i},v_{2,i}),\,i\in\{1,\cdots\,4^n\}$.
2. Compute a discretized version of the 1D connectivity kernel
   $$
   \begin{aligned}
   \tilde w(\alpha_i, \beta_j) &= \tilde J_{\alpha_i,\beta_j}\\
   &= \tilde J_{S(i),S(j)}\\
   &\stackrel{\text{def}}{=} J_{ij}\\
   &= w_U(\vec{v_i}, \vec{v_j})
   \end{aligned}
   $$
   for every pair of square locations (where we denote for simplicity of notation $S(i)=S(\vec{v_i})$).
3. Simulate the neural field in $[0,1]$ on the corresponding discretized space, with a mesh size $4^{-n}$.

@@

```{python}
#| label: fig-averaging-geom
#| fig-cap: Square populations corresponding to the segment populations before coarse-graining are colored identically when they are the same bin of 1D length $2^{-n}$. A cross marks the "average position" in each bin. Here we show $n=3$.
#| fig-subcap:
#|   - Z-mapping
#|   - Column mapping
#| layout-ncol: 2
#| echo: false

@@

	fig, ax = plt.subplots()
	ax.plot(*F.T, color='gray')
	colors = cycle(['#750087','#001997','#06bd01','#ffff00','#fe941e','#ff1e26','#fcaec5','#74d4ea','#603814','#010101','#fbf7f4'])
	for i in range(2**nrec):
		c = next(colors)
		ax.scatter(*F_[i, :, :].T, zorder=10, color=c, ec='k')
		ax.scatter(*F_[i, :, :].mean(axis=0), zorder=10, s=80, marker='X', ec='k', color=c)
	ax.set(
		xlim=(0,1), ylim=(0,1),
		xlabel='$v_1$', ylabel='$v_2$', aspect='equal',
		xticks=[0, 0.25, 0.5, 0.75, 1], yticks=[0, 0.25, 0.5, 0.75, 1])
	mktrans(fig, ax)
	breathe(ax)
	return fig, ax
